---
title: "Spacial Awareness"
format: html
editor: visual
---

## Why Spatial Analysis Matters

Modern sports are increasingly about space creation and control. Understanding these spatial concepts gives teams and analysts powerful tools to:

1. Develop more effective tactical strategies
2. Identify weaknesses in opposing team formations
3. Train players to better recognize spatial opportunities
4. Make data-driven decisions during matches

## Convexhull

Imagine stretching a rubber band around your team's defenders - that's essentially what a Convex Hull shows us!

- The colored shape that wraps around the outermost players
- How this shape expands and contracts as players move
- The total area the defense is effectively covering

What This Tells Us:
- How compact or spread out your defense is
- The spaces attackers might exploit
- How well your team maintains its defensive shape

```{r}

#| label: Convexhull

soccer_animate(td, 480, 490, "convexhull", export_gif = T, gif_name = "convexhull.gif")

```

## Voroni

Ever wondered how much space each player "owns" on the field?

- Each player has their own "territory" shown by different colors
- These territories constantly change as players move
- The boundaries show where one player's influence ends and another's begins

What This Tells Us:
- Which team controls more of the field
- Where there might be space to pass or move into
- How well positioned players are relative to each other

It's like each player has their own personal bubble, and these bubbles adjust in real-time based on everyone's position.

```{r}

#| label: Voroni

soccer_animate(td, 2112, 2122, "voronoi", export_gif = T, gif_name = "voronoi.gif")

```


